Sketch Recogniton using Particle Swarm Algorithm

### 2009-04-22 draft/System.tex
aftetr my change

\begin{figure}[]
	\centering
		\includegraphics[scale=0.8]{images/stroke3.jpg.eps}
	\caption{Input Stroke} Example of an input stroke to the system. 
	\label{fig:orignalStroke}
\end{figure}

@@

\begin{figure}[]
	\centering
		\includegraphics[scale=0.8]{images/orignalStroke.eps}
	\caption{Input Stroke} Example of an input stroke to the system. 
	\label{fig:AnotherorignalStroke}
\end{figure}

@@

The input stroke with $N$ points can be represented by set $S = \left\{ {x_1 ,x_2  \ldots x_N } \right\}$ where $x_i$ is the location of the point $i$ . The swarm algorithms consist of $M$ agents which are represented by the set 

>>>>

\begin{figure}[]
	\centering
		\includegraphics[scale=0.8]{images/stroke3.jpg.eps}
	\caption{Example of Input Stroke} Example of an input stroke to the system. 
	\label{fig:orignalStroke}
\end{figure}

@@

\begin{figure}[]
	\centering
		\includegraphics[scale=0.8]{images/orignalStroke.eps}
	\caption{Another Example of Input Stroke} Example of an input stroke to the system. 
	\label{fig:AnotherorignalStroke}
\end{figure}

@@

The input stroke with $N$ points can be represented by set $S = \left\{ {x_1 ,x_2  \ldots x_N } \right\}$ where $x_i$ is the location of the point $i$ . The swarm algorithms consist of $M$ particles which are represented by the set 
